---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
require(targets)
require(tarchetypes)
```

Target Markdown is a powerful R Markdown interface for reproducible analysis pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html walks through it in detail. This R Markdown report the example from the chapter. Try it out in both interactive and non-interactive modes, either by running the code chunks in different ways or setting the `tar_interactive` chunk option.

```{r}
tar_unscript() # delete temp files from previous run
```


# Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.

```{targets qs-globals, tar_globals = TRUE}
tar_option_set(packages = c("dplyr", "readr", "tidyr", "purrr", "magrittr", "rlang", "qualtRics"))

# replace this with sourcing functions script(s)
source(here::here("R", "utils", "qualtrics_get.R"))
source(here::here("R", "utils", "qualtrics_proc.R"))
source(here::here("R", "utils", "emo_clean.R"))
source(here::here("R", "utils", "emo_scrub.R"))
source(here::here("R", "emo_pca.R"))
source(here::here("R", "emo_model.R"))
```

# Targets

## Questionnaire data

```{targets qualtrics-get}
list(
  tar_target(qs_rd1_raw_numeric, here::here("ignore", "data", "qs_raw", "qs_rd1_raw_numeric.csv"), format = "file"),
  tar_target(qs_rd1_raw_choicetext, here::here("ignore", "data", "qs_raw", "qs_rd1_raw_choicetext.csv"), format = "file"),
  tar_target(qs_rd2_raw_numeric, here::here("ignore", "data", "qs_raw", "qs_rd2_raw_numeric.csv"), format = "file"),
  tar_target(qs_rd2_raw_choicetext, here::here("ignore", "data", "qs_raw", "qs_rd2_raw_choicetext.csv"), format = "file"),
  tar_target(qs_followup_raw_numeric, here::here("ignore", "data", "qs_raw", "qs_followup_raw_numeric.csv"), format = "file"),
  tar_target(qs_rd1, get_senpai_qualtrics(qs_rd1_raw_numeric, qs_rd1_raw_choicetext)),
  tar_target(qs_rd2, get_senpai_qualtrics(qs_rd2_raw_numeric, qs_rd2_raw_choicetext)),
  tar_target(qs_followup, get_senpai_qualtrics_followup(qs_followup_raw_numeric))
)
```

```{targets qs_allsubs, tar_simple = TRUE}
qs_bind(qs_rd1, qs_rd2, qs_followup)
```

## Task data

### Clean/preprocess data from Gorilla

```{targets task-raw-filenames}
require(tarchetypes)
task_af_raw <- tar_map(values = tibble(filename = list.files(here::here("ignore", "data", "raw", "amuse_fear_032218"),
                                              full.names = TRUE)) %>%
          separate(filename, into = c(rep(NA, times = 9), "filename_short", NA), sep = "[/.]", remove = FALSE) %>% 
          filter(endsWith(filename_short, "first")),
        tar_target(task_raw, filename, format = "file"),
        names = filename_short)

task_pn_raw <- tar_map(values = tibble(filename = list.files(here::here("ignore", "data", "raw", "pos_neg_040518"),
                                              full.names = TRUE)) %>%
          separate(filename, into = c(rep(NA, times = 9), "filename_short", NA), sep = "[/.]", remove = FALSE) %>% 
          filter(endsWith(filename_short, "first")),
        tar_target(task_raw, filename, format = "file"),
        names = filename_short)

list(task_af_raw,
     task_pn_raw)
```

```{targets task-get}
list(
  tar_target(task_af, clean_task_af(c(task_raw_amuse_cat_first,
                                      task_raw_amuse_cont_first,
                                      task_raw_fear_cat_first,
                                      task_raw_fear_cont_first))),
  tar_target(task_pn, clean_task_pn(c(task_raw_pos_cat_first,
                                      task_raw_pos_cont_first,
                                      task_raw_neg_cat_first,
                                      task_raw_neg_cont_first)))
)
```

```{targets task_allsubs, tar_simple = TRUE}
clean_task_combine(task_af, task_pn)
```

### Scrub bad boys

```{targets task-scrub}
list(
  tar_target(scrub_data, id_bad_subjs(task_allsubs, qs_allsubs)),
  tar_target(task_goodsubs, scrub_task(task_allsubs, qs_allsubs, scrub_data)),
  tar_target(badsubs, get_bad_subjs(scrub_data))
)
```

## Statistiques

### Transform questionnaire scores to PCA

```{targets pca}
list(
  tar_target(qs_goodsubs, get_pca_qs(qs_allsubs, badsubs)),
  tar_target(qs_pca, estimate_pca(qs_goodsubs)),
  tar_target(pcs_goodsubs, get_pc_scores(qs_pca, qs_goodsubs))
)
```

### Fit models? Horrifying

ONLY! modeling the unipolar data

```{targets models_prerun, tar_simple = TRUE}
read_rds(here::here("ignore", "data", "models.rds"))
```

```{targets get_model_prerun, tar_globals = TRUE}
get_model_prerun <- function (models, emo_block, resp_type) {
  models %>% 
    filter(emo_block == emo_block) %>% 
    select(model = !!paste0("model_", resp_type)) %>% 
    pull(model) %>% 
    pluck(1)
}
```


```{targets fit}
require(tarchetypes) # does this need to be in every chunk calling tarchetypes functions?

model <- tar_map(values = tibble(emo_block = c("0 to +", "0 to -"),
                                 emo_block_short = c("pos", "neg"),
                                 resp_type = c("cat", "cont")) %>% 
                   expand(nesting(emo_block, emo_block_short), resp_type),
                 #tar_toggle(get_model_prerun(models_prerun, emo_block, resp_type),
                  #          fit_emo_model(task_goodsubs, pcs_goodsubs, emo_block, resp_type)),
                 tar_target(model, get_model_prerun(models_prerun, emo_block, resp_type)),
                 names = c(emo_block_short, resp_type))

list(model)
```


# Pipeline

If you ran all the `{targets}` chunks in non-interactive mode, then your R scripts are set up to run the pipeline.

```{r}
tar_make()
```

# Output

You can retrieve results from the `_targets/` data store using `tar_read()` or `tar_load()`.

The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.
